Article title

### 2019-07-09 NAR_DRAFT.tex
add aml31 citation

\subsection{Real tumor data.}
\subsubsection{Acute Myeloid Leukemia}
We downloaded the whole genome sequence for aml31 \bkmcomment{citation and download date}.
We merged the gold and platinum lists, and define is \textit{not present} any variant for which deep sequencing was performed and zero alternate reads were observed.
This is a very conservative metric.

>>>>

\subsection{Real tumor data.}
\subsubsection{Acute Myeloid Leukemia}
We downloaded the whole genome sequence for aml31 \bkmcomment{citation and download date} \cite{Griffith2015}.
We merged the gold and platinum lists, and define is \textit{not present} any variant for which deep sequencing was performed and zero alternate reads were observed.
This is a very conservative metric.
\subsubsection{What I call the cell paper} Not sure if this will get used.
